This page and the next page should be removed

### 2021-05-04 analysis/manuscript.Rmd
add tfr

```{r setup, include=FALSE}
# Do you want to re-run the EEG preprocessing? Note that this can only be done with the raw data,
# which are available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
rerun_preproc <- TRUE

# Do you want to re-run the linear mixed-effect models? This can be done even if only the
# preprocessed single-trial data are available (from GitHub and/or the OSF). Note, however, that
# fitting all models may take 24 hours or more.
rerun_models <- FALSE

# Do you want to run the analysis for Experiment 3?
run_exp3 <- FALSE

# Load packages
library(papaja)
library(reticulate)
library(tidyverse)
library(magrittr)
library(cowplot)

# Set global chunk options
knitr::opts_chunk$set(include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10)

# Link to the bibliography file
r_refs("analysis/manuscript_files/r-references.bib")

# Source plotting functions
source("analysis/manuscript_files/functions_plots_tables.R")

# Create an export folder for results
dir.create("analysis/export", showWarnings = FALSE)

# Define ERP components of interest
comps <- tibble(
  name = c("P1", "N170", "N400"),
  tmin = c(100, 150, 400),
  tmax = c(150, 200, 700),
  roi = list(
    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
  )
)

# Define some filenames for I/O
fnames <- list(
  epochs = "analysis/export/aha-epo.fif",
  trials = "analysis/export/aha-trials.csv",
  gavgs = "analysis/export/aha-gavgs.RDS",
  conditions = "analysis/export/aha-obj-per-cond.csv",
  montage = "analysis/export/aha-montage.csv"
)
```

@@

```{python def_functions, eval=rerun_preproc}
# Import libraries
import mne
import numpy as np

@@

# Define function for preprocessing a list of participants
def preproc_all(
    vhdr_fnames,
    metadatas,
    output_fname,
    n_components,
    method,
    l_freq,
    h_freq,
    event_id,
    tmin,
    tmax,
    baseline,
    reject,
):
    # Do the actual preprocessing
    epochs = [
        preproc(
            vhdr_fname=vhdr_fname,
            metadata=metadata,
            n_components=n_components,
            method=method,
            l_freq=l_freq,
            h_freq=h_freq,
            event_id=event_id,
            tmin=tmin,
            tmax=tmax,
            baseline=baseline,
            reject=reject,
        )
        for vhdr_fname, metadata in zip(vhdr_fnames, metadatas)
    ]
    # Concatenate all participants and save
    epochs = mne.epochs.concatenate_epochs(epochs)
    epochs.save(output_fname, overwrite=True)
    # Return the epochs without loading the actual data
    epochs = mne.read_epochs(output_fname, preload=False)
    return epochs

# Define function to compute averaged waveforms by part and condition
def compute_evokeds(epochs_fname, grand=True, data_only=True):
    # Read preprocessed epochs
    epochs = mne.read_epochs(epochs_fname)
    # Define lists of participants, parts, and conditions
    ps = epochs.metadata["participant"].unique()
    pts = ["I", "II", "III"]
    cns = ["Informed", "Naive"]
    # Define function to compute a single by-participant waveform
    def compute_evoked(epochs, pt, cn, p):
        query = 'participant == "' + p + '" and part == "' + pt + '" and condition == "' + cn + '"'
        return epochs[query].average()

    # Create a dict with by-participant waveforms nested in conditions nested in parts
    avgs = {pt: {cn: [compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
    # If needed, compute grand-averaged waveforms across participants
    if grand:
        avgs = {pt: {cn: mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
    # If needed, extract only the data from the evoked MNE objects
    if data_only:
        if grand:
            avgs = {pt: {cn: avgs[pt][cn].data for cn in cns} for pt in pts}
        else:
            ps_num = range(0, len(ps))
            avgs = {pt: {cn: [avgs[pt][cn][p].data for p in ps_num] for cn in cns} for pt in pts}
    return avgs

@@

```{r exp1-preproc, eval=rerun_preproc}
# Define function for reading and formatting the behavioral data
read_behav <- function(txt_fname) {
  # Read the log file
  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
  # Rename columns for participant and item IDs
  dat %<>% rename(participant = VPNummer, item = StimID) %>%
    # Add a column for the part of the experiment
    mutate(part = case_when(
      Wdh %in% c(211, 231) ~ "I",
      Wdh %in% c(212, 232) ~ "II",
      Wdh %in% c(213, 233) ~ "III",
      Wdh == 234 ~ "IV"
    ) %>% as_factor()) %>%
    # Remove filler stimuli (i.e.,well-known objects)
    filter(bek_unbek != "bekannt")
  # Assign stimuli to conditions based on keywords and button presses
  excl_known <- dat %>%
    filter(part == "I" & Tastencode %in% c(201, 251)) %>%
    pull(item)
  excl_informed <- dat %>%
    filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>%
    pull(item)
  excl_naive <- dat %>%
    filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>%
    pull(item)
  informed <- dat %>%
    filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>%
    pull(item)
  naive <- dat %>%
    filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>%
    pull(item)
  # Create a new condition for the experimental condition
  dat %<>% mutate(condition = case_when(
    item %in% excl_known ~ "Excl_known",
    item %in% excl_informed ~ "Excl_informed",
    item %in% excl_naive ~ "Excl_naive",
    item %in% informed ~ "Informed",
    item %in% naive ~ "Naive"
  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
  # In Experiment 3, we need an additional column for position (upright vs. inverted)
  if ("richtig_inv" %in% dat$Bed) {
    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
      # Return only relevant columns
      select(part, position, condition, participant, item, RT)
  } else {
    # Return only relevant columns
    dat %<>% select(part, condition, participant, item, RT)
  }
  return(dat)
}

# Read behavioral data from two batches of participants
paste0("data/rt/exp", 1:2) %>%
  map(list.files, pattern = ".txt", full.names = TRUE) %>%
  map(map, read_behav) -> behav

# Avoid duplicate participant labels across the two batches
behav[[2]] %<>% map(mutate, participant = paste0(participant, "_2"))

# Merge into a single list
behav %<>% flatten()

# Define global parameters for EEG preprocessing
preproc_params <- list(
  # Number of ICA components
  n_components = as.integer(15),
  # ICA methods
  method = "fastica",
  # Lower edge of pass-band filter
  l_freq = 0.1,
  # Upper edge of pass-band filter
  h_freq = 30,
  # Event trigger codes
  event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
  # Beginning of epochs in s
  tmin = -0.5,
  # End of epochs in s
  tmax = 1.498,
  # Baseline interval in s
  baseline = tuple(-0.2, 0),
  # Artifact rejection threshold in microvolts
  reject = dict(eeg = 200)
)

# Preprocess the EEG for Experiment 1 in Python
paste0("data/eeg/exp", 1:2) %>%
  list.files(pattern = ".vhdr", full.names = TRUE) %>%
  exec(
    .fn = py$preproc_all,
    vhdr_fnames = .,
    metadatas = behav,
    output_fname = fnames$epochs,
    !!!preproc_params
  ) -> epochs

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs_fname = fnames$epochs) %>%
  set_names(comps$name) %>%
  bind_cols(epochs$metadata, .) %T>%
  write_tsv(fnames$trials) -> aha

# Compute grand averages per part and condition
py$compute_evokeds(epochs_fname = fnames$epochs, grand = TRUE, data_only = TRUE) %>%
  saveRDS(fnames$gavgs)

# Backup number of stimuli assigned to each condition for all participants
map(behav, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(aha$participant), .before = 1) %>%
  write_csv(fnames$conditions)

# Get standard EasyCap electrode positions and project to 2D space
py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
  list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
  read_tsv(col_types = cols()) %>%
  rename(electrode = Site) %>%
  inner_join(tibble(electrode = epochs$ch_names), ., by = "electrode") %>%
  mutate(
    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
  ) %>%
  write_csv(fnames$montage)
```

```{r exp1-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/aha-trials.csv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> aha

@@

# Specify model formula and follow-up contrasts
form <- erp ~ part * condition +
  (part * condition | participant) +
  (part * condition | item)
specs <- pairwise ~ condition | part

# Calculate linear mixed-effects models and contrasts
map(comps$name, function(comp, formula = form, data = aha, specs = specs) {
  require(afex)
  require(emmeans)
  data %<>% rename(erp = all_of(comp))
  mod <- mixed(
    formula,
    data,
    method = "S",
    check_contrasts = FALSE,
    all_fit = TRUE
  )
  em <- emmeans(mod, specs = specs, infer = TRUE, data = data)
  modlist <- list(
    model = mod,
    anova = anova(mod),
    summary = summary(mod),
    means = as.data.frame(em$means),
    contrasts = as.data.frame(em$contrasts)
  )
}) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/aha_models_freq.RDS") -> mods_freq
```

```{r exp1-import}
# Load average number of objects per condition
(read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp1)

# Load preprocessed single-trial data
read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> aha

# Check number of rejected epochs
aha %>%
  group_by(participant) %>%
  tally() %>%
  mutate(n = 360 - n) %>%
  pull(n) -> rejected_exp1
mean(rejected_exp1)    # Mean
median(rejected_exp1)  # Median
range(rejected_exp1)   # Range

# Load grand-averaged ERPs and linear mixed models
evokeds_exp1 <- readRDS("analysis/export/exp1-gaverages.RDS")
models_exp1 <- readRDS("analysis/export/exp1-models.RDS")
```

@@

```{python tfr, eval=FALSE}
import mne
import numpy as np
#import matplotlib.pyplot as plt

# epochs = preproc(
#   vhdr_fname="data/exp1/eeg/Vp0004.vhdr",
#   metadata=r.aha.query("participant == 'VP_04'"),
#   n_components=15,
#   method="fastica",
#   l_freq=None,
#   h_freq=None,
#   event_id=dict(match=221, mismatch=222),
#   tmin=-0.5,
#   tmax=1.498,
#   baseline=(-0.2, 0),
#   reject=dict(eeg=200)
# )
# epochs.save("analysis/export/vp04-epo.fif")

epochs = mne.read_epochs("analysis/export/unf-exp1-epo.fif")

@@

```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
# Load sample time points and electrode montage
montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())

@@

# Backup epochs to the export folder
epochs_exp2$save("analysis/export/exp2-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp2) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
  write_tsv("analysis/export/exp2-data.tsv") -> data_exp2

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp2-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp2, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
  write_tsv("analysis/export/exp2-objects.tsv")

@@

```{r exp2-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp2

@@

# Compute the models for Experiment 2
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp2,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp2-models.RDS") -> models_exp2
```

```{r exp2-import}
# Load average number of objects per condition
(read_tsv("analysis/export/exp2-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp2)

# Load preprocessed single-trial data
read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp2

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp2 <- readRDS("analysis/export/exp2-gaverages.RDS")
models_exp2 <- readRDS("analysis/export/exp2-models.RDS")
```

@@

# Apply the function to compute the joint models for Experiments 1 and 2
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_subs,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/joint-models.RDS") -> models_joint
```

```{r joint-table, include=TRUE, results="asis"}
# Load linear mixed models
models_joint <- readRDS("analysis/export/joint-models.RDS")

@@

# Apply the function to re-compute the joint models
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_control,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/joint-control-models.RDS") -> models_joint_control
```

@@

# Load linear mixed models
models_joint_control <- readRDS("analysis/export/joint-control-models.RDS")

@@

# Backup epochs to the export folder
epochs_exp3$save("analysis/export/exp3-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp3) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
  write_tsv("analysis/export/exp3-data.tsv") -> data_exp3

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp3-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp3, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
  write_tsv("analysis/export/exp3-objects.tsv")

>>>>

```{r setup, include=FALSE}
# Load packages
library(lmerTest)
library(emmeans)
library(papaja)
library(reticulate)
library(tidyverse)
library(magrittr)
library(cowplot)

# Load helper functions for plots and tables
source("analysis/manuscript_files/functions_plots_tables.R")

# Load bibliography file
r_refs("analysis/manuscript_files/r-references.bib")

# Set some global chunk options
knitr::opts_chunk$set(
  include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10
)
```

@@

```{python, erp_funcs}
# Import libraries
import mne
import numpy as np

@@

# Define function for preprocessing a list of participants
def preproc_all(
    vhdr_fnames,
    metadatas,
    output_fname,
    n_components,
    method,
    l_freq,
    h_freq,
    event_id,
    tmin,
    tmax,
    baseline,
    reject,
):
    # Do the actual preprocessing
    epochs = [
        preproc(
            vhdr_fname=vhdr_fname,
            metadata=metadata,
            n_components=n_components,
            method=method,
            l_freq=l_freq,
            h_freq=h_freq,
            event_id=event_id,
            tmin=tmin,
            tmax=tmax,
            baseline=baseline,
            reject=reject,
        )
        for vhdr_fname, metadata in zip(vhdr_fnames, metadatas)
    ]
    # Concatenate all participants and save
    epochs = mne.epochs.concatenate_epochs(epochs)
    epochs.save(output_fname, overwrite=True)
    del epochs
    # Return the epochs without loading the actual data
    epochs = mne.read_epochs(output_fname, preload=False)
    return epochs

# Define function to compute averaged waveforms by part and condition
def compute_evokeds(epochs_fname, grand=True, data_only=True):
    # Read preprocessed epochs
    epochs = mne.read_epochs(epochs_fname)
    # Define lists of participants, parts, and conditions
    ps = epochs.metadata["participant"].unique()
    pts = ["I", "II", "III"]
    cns = ["Informed", "Naive"]
    # Define function to compute a single by-participant waveform
    def compute_evoked(epochs, pt, cn, p):
        query = 'participant == "' + p + '" and part == "' + pt + '" and condition == "' + cn + '"'
        return epochs[query].average()
    # Create a dict with by-participant waveforms nested in conditions nested in parts
    avgs = {pt: {cn: [compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
    # If needed, compute grand-averaged waveforms across participants
    if grand:
        avgs = {pt: {cn: mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
    # If needed, extract only the data from the evoked MNE objects
    if data_only:
        if grand:
            avgs = {pt: {cn: avgs[pt][cn].data for cn in cns} for pt in pts}
        else:
            ps_num = range(0, len(ps))
            avgs = {pt: {cn: [avgs[pt][cn][p].data for p in ps_num] for cn in cns} for pt in pts}
    return avgs

@@

```{r, preprocessing}
# Define ERP components of interest
comps <- tibble(
  name = c("P1", "N170", "N400"),
  tmin = c(100, 150, 400),
  tmax = c(150, 200, 700),
  roi = list(
    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
  )
)

# Define some filenames for I/O
fnames <- list(
  epochs = "data/processed/aha-epo.fif",
  epochs_unf = "data/processed/aha-unf-epo.fif",
  trials = "data/processed/aha-trials.csv",
  gavgs = "data/processed/aha-gavgs.RDS",
  conditions = "data/processed/aha-obj-per-cond.csv",
  montage = "data/processed/aha-montage.csv",
  models_freq = "data/processed/aha-models-freq.RDS"
)

# Define parameters for EEG preprocessing
preproc_params <- list(
  # Number of ICA components
  n_components = as.integer(15),
  # ICA methods
  method = "fastica",
  # Lower edge of pass-band filter
  l_freq = 0.1,
  # Upper edge of pass-band filter
  h_freq = 30,
  # Event trigger codes
  event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
  # Beginning of epochs in s
  tmin = -0.5,
  # End of epochs in s
  tmax = 1.498,
  # Baseline interval in s
  baseline = tuple(-0.2, 0),
  # Artifact rejection threshold in microvolts
  reject = dict(eeg = 200)
)

# Check if single-trial data are available
if (file.exists(fnames$trials)) {

  # If so, load preprocessed single-trial data
  read_tsv(fnames$trials, col_types = cols()) %>%

    # Factorize columns
    mutate(
      part = factor(part, levels = c("I", "II", "III")),
      condition = factor(condition, levels = c(
        "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
      )),
      participant = factor(participant),
      item = factor(item)
    ) -> aha

} else {

  # If not, we preprocess the behvarioral and EEG data
  paste0("data/raw/rt/exp", 1:2) %>%
    map(list.files, pattern = ".txt", full.names = TRUE) %>%
    map(map, function(txt_fname) {

      # Read the behavioral log file
      suppressWarnings(read_tsv(txt_fname, col_types = cols())) %>%

        # Rename columns for participant and item IDs
        rename(participant = VPNummer, item = StimID) %>%

        # Add a column for the part of the experiment
        mutate(part = case_when(
          Wdh %in% c(211, 231) ~ "I",
          Wdh %in% c(212, 232) ~ "II",
          Wdh %in% c(213, 233) ~ "III",
          Wdh == 234 ~ "IV"
        ) %>% as_factor()) %>%

        # Remove filler stimuli (i.e.,well-known objects)
        filter(bek_unbek != "bekannt") -> dat

      # Assign stimuli to conditions based on keywords and button presses in Part II
      excl_known <- dat %>%
        filter(part == "I" & Tastencode == 201) %>%
        pull(item)
      excl_informed <- dat %>%
        filter(part == "II" & Bed == "richtig" & !Tastencode %in% c(201, 202)) %>%
        pull(item)
      excl_naive <- dat %>%
        filter(part == "II" & Bed == "falsch" & !Tastencode %in% c(203, 204)) %>%
        pull(item)
      informed <- dat %>%
        filter(part == "II" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>%
        pull(item)
      naive <- dat %>%
        filter(part == "II" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>%
        pull(item)

      # Create a new condition for these experimental condition
      dat %<>% mutate(condition = case_when(
        item %in% excl_known ~ "Excl_known",
        item %in% excl_informed ~ "Excl_informed",
        item %in% excl_naive ~ "Excl_naive",
        item %in% informed ~ "Informed",
        item %in% naive ~ "Naive"
      ) %>% factor(levels = c(
        "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
      ))) %>%

        # Return only relevant columns
        select(part, condition, participant, item, RT) %>%
        return()
    }) -> behav

  # Avoid duplicate participant labels across the two experiments
  behav[[2]] %<>% map(mutate, participant = paste0(participant, "_2"))

  # Merge behavioral data for all participants into a single list
  behav %<>% flatten()

  # List BrainVision header file names for preprocessing
  paste0("data/raw/eeg/exp", 1:2) %>%
    list.files(pattern = ".vhdr", full.names = TRUE) -> fnames$vhdr

  # # Do the actual preprocessing in MNE-Python
  # exec(
  #   .fn = py$preproc_all,
  #   vhdr_fnames = fnames$vhdr,
  #   metadatas = behav,
  #   output_fname = fnames$epochs,
  #   !!!preproc_params
  # ) -> epochs
  # 
  # # Compute mean ERP amplitudes and bind to the behavioral data
  # pmap_dfc(comps, py$compute_erps, epochs_fname = fnames$epochs) %>%
  #   set_names(comps$name) %>%
  #   bind_cols(epochs$metadata, .) %T>%
  #   write_tsv(fnames$trials) -> aha
  # 
  # # Compute grand averages per part and condition
  # py$compute_evokeds(epochs_fname = fnames$epochs, grand = TRUE, data_only = TRUE) %>%
  #   saveRDS(fnames$gavgs)
  # 
  # # Backup number of stimuli assigned to each condition for all participants
  # map(behav, function(x) table(x$condition) / 3) %>%
  #   bind_rows() %>%
  #   mutate(Participant = unique(aha$participant), .before = 1) %>%
  #   write_csv(fnames$conditions)
  # 
  # # Get standard EasyCap electrode positions and project to 2D space
  # py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
  #   list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
  #   read_tsv(col_types = cols()) %>%
  #   rename(electrode = Site) %>%
  #   inner_join(tibble(electrode = epochs$ch_names), ., by = "electrode") %>%
  #   mutate(
  #     x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
  #     y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
  #   ) %>%
  #   write_csv(fnames$montage)

  # Do the preprocessing again, this time without filtering (for TFR)
  preproc_params$l_freq <- py_none()
  preproc_params$h_freq <- py_none()
  preproc_params$reject <- py_none()
  exec(
    .fn = py$preproc_all,
    vhdr_fnames = fnames$vhdr,
    metadatas = behav,
    output_fname = fnames$epochs_unf,
    !!!preproc_params
  ) -> epochs_unf
}

# Check number of rejected epochs
aha %>%
  group_by(participant) %>%
  tally() %>%
  mutate(n = 360 - n) %>%
  pull(n) -> rejected
mean(rejected)    # Mean
median(rejected)  # Median
range(rejected)   # Range
```

```{r, models_freq}
# Remove any trials excluded from conditions
aha %>%
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> aha

@@

# Specify model formula
form <- erp ~ part * condition +
  (part * condition | participant) +
  (part * condition | item)

# Specify follow-up comparisons
specs <- pairwise ~ condition | part

# Calculate linear mixed-effects models and follow-up comparisons
map(comps$name, function(comp, formula = form, data = aha, specs = specs) {
  data %<>% rename(erp = all_of(comp))
  mod <- lmer(formula, data, all_fit = TRUE)
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  em <- emmeans(mod, specs = specs, infer = TRUE, data = data)
  modlist <- list(
    model = mod,
    anova = anova(mod),
    summary = summary(mod),
    means = as.data.frame(em$means),
    contrasts = as.data.frame(em$contrasts)
  )
}) %>%
  set_names(comps$name) %T>%
  saveRDS(fnames$models_freq) -> mods_freq
```

@@

```{python, tfr}
from mne.time_frequency import tfr_morlet
from mne.channels import find_ch_adjacency
from mne.stats import spatio_temporal_cluster_test

epochs_unf = mne.read_epochs(r.fnames["epochs_unf"])
epochs_ptII_informed = epochs_unf["part == 'II' & condition == 'Informed'"]
epochs_ptII_naive = epochs_unf["part == 'II' & condition == 'Naive'"]

evokeds = compute_evokeds(
  epochs_fname=r.fnames["epochs_unf"], grand=False, data_only=False
)

evokeds_informed = evokeds["II"]["Informed"]
evokeds_naive = evokeds["II"]["Naive"]

X1 = np.array([evokeds.data for evokeds in evokeds_informed])
X2 = np.array([evokeds.data for evokeds in evokeds_naive])
X1 = np.transpose(X1, [0, 2, 1])
X2 = np.transpose(X2, [0, 2, 1])
X = [X1, X2]

adjacency, ch_names = find_ch_adjacency(evokeds["II"]["Informed"][0].info, ch_type="eeg")

cluster_stats = spatio_temporal_cluster_test(
  X=X,
  n_permutations=1000,
  tail=0,
  n_jobs=1,
  buffer_size=None,
  adjacency=adjacency,
)

p_accept = 0.05
T_obs, clusters, p_values, _ = cluster_stats
good_cluster_inds = np.where(p_values < p_accept)[0]

freqs = np.logspace(*np.log10([6, 35]), num=8)
n_cycles = freqs / 2.

tfr_ptII_informed = tfr_morlet(
  epochs_ptII_informed,
  freqs=freqs,
  n_cycles=n_cycles,
  decim=2,
  return_itc=False,
  average=False,
)
tfr_ptII_naive = tfr_morlet(
  epochs_ptII_naive,
  freqs=freqs,
  n_cycles=n_cycles,
  decim=2,
  return_itc=False,
  average=False,
)

tfr_ptII_informed.apply_baseline(mode='ratio', baseline=(None, 0))
tfr_ptII_naive.apply_baseline(mode='ratio', baseline=(None, 0))

adjacency, ch_names = find_ch_adjacency(epochs_ptII_informed.info, ch_type="eeg")

spatio_temporal_cluster_test(X, n_permutations=1000,
                                             threshold=threshold, tail=1,
                                             n_jobs=1, buffer_size=None,
                                             adjacency=adjacency)

```{python tfr_old, eval=FALSE}
import mne
import numpy as np
#import matplotlib.pyplot as plt

# epochs = preproc(
#   vhdr_fname="data/exp1/eeg/Vp0004.vhdr",
#   metadata=r.aha.query("participant == 'VP_04'"),
#   n_components=15,
#   method="fastica",
#   l_freq=None,
#   h_freq=None,
#   event_id=dict(match=221, mismatch=222),
#   tmin=-0.5,
#   tmax=1.498,
#   baseline=(-0.2, 0),
#   reject=dict(eeg=200)
# )
# epochs.save("data/processed/vp04-epo.fif")

epochs = mne.read_epochs("data/processed/unf-exp1-epo.fif")

@@

```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
# Load sample time points and electrode montage
montage <- read_csv("data/processed/aha-montage.csv", col_types = cols())

@@

# Backup epochs to the export folder
epochs_exp2$save("data/processed/exp2-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp2) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
  write_tsv("data/processed/exp2-data.tsv") -> data_exp2

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
  saveRDS("data/processed/exp2-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp2, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
  write_tsv("data/processed/exp2-objects.tsv")

@@

```{r exp2-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("data/processed/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp2

@@

# Compute the models for Experiment 2
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp2,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("data/processed/exp2-models.RDS") -> models_exp2
```

```{r exp2-import}
# Load average number of objects per condition
(read_tsv("data/processed/exp2-objects.tsv", col_types = cols()) %>%
   summarise(across(.cols = -Participant, .fns = mean)) %>%
   slice(1) %>% unlist() -> objects_exp2)

# Load preprocessed single-trial data
read_tsv("data/processed/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp2

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp2 <- readRDS("data/processed/exp2-gaverages.RDS")
models_exp2 <- readRDS("data/processed/exp2-models.RDS")
```

@@

# Apply the function to compute the joint models for Experiments 1 and 2
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_subs,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("data/processed/joint-models.RDS") -> models_joint
```

```{r joint-table, include=TRUE, results="asis"}
# Load linear mixed models
models_joint <- readRDS("data/processed/joint-models.RDS")

@@

# Apply the function to re-compute the joint models
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_control,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("data/processed/joint-control-models.RDS") -> models_joint_control
```

@@

# Load linear mixed models
models_joint_control <- readRDS("data/processed/joint-control-models.RDS")

@@

# Backup epochs to the export folder
epochs_exp3$save("data/processed/exp3-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp3) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
  write_tsv("data/processed/exp3-data.tsv") -> data_exp3

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
  saveRDS("data/processed/exp3-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp3, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
  write_tsv("data/processed/exp3-objects.tsv")
